Datasheet for Unveiling Vulnerabilities

### 2024-04-25 paper/datasheet_template.qmd
Reviewed and fixed typos in datasheet

---
title: "Datasheet for Unveiling Vulnerabilities"
subtitle: "An Analysis of Causes of Death Across Age Groups and Genders Within Toronto's Homelessness Population"
author: "Faiza Imam"
thanks: "Code and data are available at: https://github.com/fazim07/deaths_gender"
date: today
date-format: long
abstract: "This datasheet describes the motivations and composition of homesless death by cause data set obtained from OpenData Toronto. It also describes collection process, cleaning process, uses, distribution, and maintenance of the data sets."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The data set comes in a CSV, JSON or Excel file no DOIs.

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Opendata Toronto portal will host and support the dataset while Opendata Toronto updates the data set.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- Can be contacted via email from Opendata Toronto

>>>>

---
title: "Datasheet for Unveiling Vulnerabilities"
subtitle: "An Analysis of Causes of Death Across Age Groups and Genders Within Toronto's Homelessness Population"
author: "Faiza Imam"
thanks: "Code and data are available at: https://github.com/fazim07/deaths_gender"
date: today
date-format: long
abstract: "This datasheet describes the motivations and composition of homesless death by cause dataset obtained from OpenData Toronto. It also describes collection process, cleaning process, uses, distribution, and maintenance of the datasets."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset comes in a CSV, JSON or Excel file no DOIs.

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Opendata Toronto portal will host and support the dataset while Opendata Toronto updates the dataset.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- Can be contacted via email from Opendata Toronto
